On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-04 MS.tex
Change in ms
Change in Fig S8 and Fig2 legende in ms

We first developed a snapshot of the literature, to assess potential to recover useufl data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter. Line segments indicate the size range (max., min.) for the plants used to measure growth. Article IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors, while line styles denote growth form. The vertical lines indicate the thresholds used in our analysis. Results shown here are the ``complete'' dataset (see methods for details).}
\label{fig:fig2}
\end{figure}

@@

%TODO: I suggest keeping this table, but merging the two right hand columns. The text in the explanation column mostly just repeats material that is presented elsewhere, so best to just say briefly where to find it.
\clearpage
\begin{table}[h!]
\centering
\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{5cm}p{0.8cm}p{9cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed? \\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& We provided complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
  2.& Reporting inclusion/exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method. The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variation, and stage as a fixed effect. See details in sub-section "Stage effect" in material and methods. Results are shown in Fig3.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix D.\\
 6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
 7.& Multifactorial analysis of explanatory variable	& yes & We checked if no one of several other explanatory moderators (i.e. growth measurement, experiment type or growth form) would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See FigA4b and FigA6.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number). See details of methods and results in Appendix D and FigA7\\
  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig3 and FigA5 \\
  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix D and FigA9.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sub-section ``Availability of code and data'' in material and methods\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	See sub-section ``Availability of code and data'' in material and methods. The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses. \\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github. See ``Availability of code and data'', section "Statistical analysis" in material and methods. \\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{fig:figA3}
\end{figure}

>>>>

We first developed a snapshot of the literature, to assess potential to recover useful data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter. Line segments indicate the size range (max., min.) for the plants used to measure growth. Article IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors. The vertical lines indicate the thresholds used in our analysis. "*" indicated when a stage reassignment is needed. Dots on right side of the graph indicate cases where plants had different growth form. Results shown here are the ''complete'' dataset (see methods for details).}
\label{fig:fig2}
\end{figure}

@@

\clearpage
\begin{table}[h!]
\centering
\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed? \\
  \hline
  1.& Reporting full details of bibliographic searches & yes	& We provided complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
  2.& Reporting inclusion or exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method. The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variation, and stage as a fixed effect. See details in sub-section "Stage effect" in material and methods. Results are shown in Fig3.\\
 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix D.\\
 6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
 7.& Multifactorial analysis of explanatory variable	& yes & We checked if no one of several other explanatory moderators (i.e. growth measurement, experiment type or growth form) would not consistenly be a strongest predictor of the data. We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See FigA4b and FigA6.\\
  8.& Testing for publication bias &	yes	& We used several methods (i.e. funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number). See details of methods and results in Appendix D and FigA7\\
  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig3 and FigA5 \\
  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix D and FigA9.\\
  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used &	yes	& See sub-section ``Availability of code and data'' in material and methods\\
 13.& Providing reference list of primary studies included in the analysis &	yes &	See sub-section ``Availability of code and data'' in material and methods. The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses. \\
  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github. See ``Availability of code and data'', section "Statistical analysis" in material and methods. \\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Results shown here are from the ``complete'' dataset (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and green
points to juveniles.}
\label{fig:figA3}
\end{figure}
